Project Setup

### 2024-11-26 setup.qmd
Provide additional references

Generally, metadata are either stored embedded into the data or externally, for example, in a separate file. We will use the "[frictionless data](https://frictionlessdata.io/)" standard, where metadata are stored separately.

@@

- "Tidy design principles" [@Wickham2023Design]
- "The Good Research Code Handbook" [@Mineault2021]
- "The Art of UNIX Programming" [@Raymond2003]

>>>>

Generally, metadata are either stored embedded into the data or externally, for example, in a separate file. We will use the "[frictionless data](https://frictionlessdata.io/)" standard, where metadata are stored separately. Another alternative would be [RO-Crate](https://www.researchobject.org/ro-crate/).

@@

- "Tidy design principles" [@Wickham2023Design]
- "The Good Research Code Handbook" [@Mineault2021]
- "Quality assurance of code for analysis and research" [@UKGovernment2020]
- "The Art of UNIX Programming" [@Raymond2003]
